Coeficientes para la corrección de bias

### 2020-10-23 analysis/chapters/coeficientes.Rmd
Nueva versión post reunion 23/10/2020

>>>>

```{r}
diag_rad %>% 
  .[qc == 0 & channel %in% c(5:8)] %>% 
  melt(measure.vars = c("tbc", "tbcnob")) %>% 
  .[, .(ob_mean = mean(value, na.rm = TRUE),
       ob_sd = sd(value, na.rm = TRUE)), by = .(date, sensor, channel, exp, variable)] %>% 
  # melt(measure.vars = c("ob_mean", "ob_sd"),  variable.name = "estadistico", 
  #      value.name = "valor") %>% 
ggplot(aes(date, ob_mean)) +
  geom_hline(yintercept = 0) +
  geom_point(aes(color = exp)) +
  geom_line(aes(color = exp, linetype = variable)) +
  scale_color_manual(values = c("darkorange", cyan), labels = c("pre-RAD1", "pre-RAD2")) +
  scale_linetype_discrete(labels = c("Bias corregido", "Sin corrección")) +
  facet_grid(channel~sensor, scales = "free_y") +
  labs(y = NULL, x = NULL, color = NULL, linetype = NULL) +
  theme_minimal()
```
